Live Functional Programming with Typed Holes

### 2018-03-07 calculus.tex
split metatheory into two sections
calculus edit

>>>>

Talk about weak vs strong conversion vs sharing -- see \url{http://gallium.inria.fr/~maranget/papers/jwk60.pdf} and cited work in the intro. See also \url{https://www.lri.fr/~blsk/Docs/Balabonski-FullLaziness-POPL12.pdf}?? Original Church-Rosser paper -- \url{http://www.ams.org/journals/tran/1936-039-03/S0002-9947-1936-1501858-0/S0002-9947-1936-1501858-0.pdf}.
